Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
reviewed 5 Conclusions
reviewed 4.4 Threats to validity
+todo

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
and alongside completeness we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.

Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.

The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.

@@

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other in the benchmark coverage and together 
solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
and alongside completeness \todo{are we actually complete? for instance, abstraction refinement might not be successful (we do TO)} we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks. 
%
Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high. 
%
The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.

@@

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers.
